Considering scale in multilayer animal social networks

### 2020-06-21 paper/manuscript.Rmd
add dates directly

<!--QW: what makes it ordinal again? Is it ordinal OR continuous? -->
The ordinal multilayer network generated indicated within-year time windows of
increased caribou sociality. <!--QW: I'm not sure what you are trying to say in this first sentence. Is it that there are distinct within-year time windows where social network metrics increased? -->
Edge overlap was higher in time windows 1, 6-11 and
15-20 than in time windows 2-5 and 12-15  (Figure \@ref(fig:temp) A). <!--QW: I'm not sure about using the window number - it doesn't really mean anyhting. Can you use actual dates?--> Time
windows of higher edge overlap, between approximately October and May, had
correspondingly higher graph strength compared to time windows of lower edge
overlap, between approximately May and October (Figure \@ref(fig:temp) C). Graph
strength peaked across the time series in periods 9 and 10. These results
suggest that ordinal multilayer networks can effectively capture discrete time
windows of aggregation and dissaggregation related to resource availability, and
highlight the importance of carefully selecting the temporal scale of analysis.

As the number of observations used to generate multilayer networks increased,
individuals became more connected and variance in metrics decreased. <!--QW: I think throughout you want to say "variance decreased" instead of "stabilized" -->
Graph strength across individuals in all three habitat layers was highly
variable at low number of observations and stabilized after ~100 observations
(Figure \@ref(fig:nobs) A). Edge overlap increased across all three habitat
layers with increasing number of observations (Figure \@ref(fig:nobs) B).
Similarly, multidegree for all individuals increased quickly between 10 and 100
observations, and continued to increase until 1000 observations (Figure
\@ref(fig:nobs) C). Given the observed trend of these multilayer metrics
stabilizing after a certain number of observations are included, the results
suggest this sensitivity method could be useful for determining the number of
observations necessary for sufficiently describing social dynamics across
contexts.

>>>>

<!--QW: what makes it ordinal again? Is it ordinal OR continuous? -->
The ordinal multilayer network indicated within-year time windows where social 
network metrics increased. Edge overlap was higher in time windows 1, 6-11 and 15-20 (between `r timedefs[timecut == 1, paste(mindate, maxdate, sep = ' and ')]`,  
`r timedefs[timecut %in% 6:11, paste(min(mindate), max(maxdate), sep = ' and ')]`
and `r timedefs[timecut %in% 15:20, paste(min(mindate), max(maxdate), sep = ' and ')]`) 
than in time windows 2-5 and 12-15 (between `r timedefs[timecut %in% 2:5, paste(min(mindate), max(maxdate), sep = ' and ')]` 
and `r timedefs[timecut %in% 12:15, paste(min(mindate), max(maxdate), sep = ' and ')]`)
(Figure \@ref(fig:temp) A). Time windows of higher edge overlap, between approximately October and June, had correspondingly higher graph strength 
compared to time windows of lower edge overlap, between approximately June 
and October (Figure \@ref(fig:temp) C). Graph strength peaked across the time 
series between  `r timedefs[timecut %in% 9:10, paste(min(mindate), max(maxdate), sep = ' and ')]`. 
These results suggest that ordinal multilayer networks can effectively capture discrete time windows of aggregation and dissaggregation related to resource availability, and highlight the importance of carefully selecting the temporal scale of analysis.

As the number of observations used to generate multilayer networks increased,
individuals became more connected and variance in metrics decreased.<!--QW: I think throughout you want to say "variance decreased" instead of "stabilized" --> Graph strength across individuals in all three habitat layers was highly
variable at low number of observations and stabilized after ~100 observations
(Figure \@ref(fig:nobs) A). Edge overlap increased across all three habitat
layers with increasing number of observations (Figure \@ref(fig:nobs) B).
Similarly, multidegree for all individuals increased quickly between 10 and 100
observations, and continued to increase until 1000 observations (Figure
\@ref(fig:nobs) C). Given the observed trend of these multilayer metrics
stabilizing after a certain number of observations are included, the results
suggest this sensitivity method could be useful for determining the number of
observations necessary for sufficiently describing social dynamics across
contexts.
